Taking uncertainty in word embedding bias estimation seriously: a bayesian approach

### 2022-07-28 paperDraft/paperDraft4.tex
results added to v 7

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames,enabledeprecatedfontcommands, twocolumn]{scrartcl}
\title{Taking uncertainty in word embedding bias estimation seriously: a
bayesian approach}
\author{Alicja Dobrzeniecka and Rafal Urbaniak}
\date{}

@@

Modern Natural Language Processing (NLP) models are used to complete
various tasks such as providing email filters, smart assistants, search
results, language translations, text analytics and so on. All of them
need as an input words represented by means of numbers which is
accomplished with word embeddings, in which particular lexical units are
repesented as vectors of real numbers. It has been suggested {[}1--6{]}
that in the learning process such models can learn implicit biases that
reflect harmful stereotypical thinking. A large chunk of the literature
on the topic focuses on the geometry of the learnt word embeddings; in
particular, unusually low (cosine) proximity of words belonging,
intuitively, to a stereotype, is taken as a sign that this stereotype
has been built into a given embedding. This methodology will be in the
focus of our paper.

\begin{itemize}
\tightlist
\item
  undesirable bias with respect to a certain groups words if
  stereotypically connected words (for stereotypes that we don't want to
  be used or relied on in downstream tasks) are systematically closer to
  each other. + EXAMPLE
\end{itemize}

\hypertarget{semantical-interpretation}{%
\subsection{Semantical interpretation}\label{semantical-interpretation}}

@@

\hypertarget{weat-and-mac-measures}{%
\subsection{WEAT and MAC measures}\label{weat-and-mac-measures}}

@@

\hypertarget{non-statistical-problems-with-cosine-based-measures-of-bias}{%
\subsection{Non-statistical problems with cosine-based measures of
bias}\label{non-statistical-problems-with-cosine-based-measures-of-bias}}

@@

\hypertarget{statistical-issues}{%
\subsection{Statistical issues}\label{statistical-issues}}

@@

\hypertarget{weat}{%
\subsection{WEAT}\label{weat}}

\hypertarget{mac}{%
\subsection{MAC}\label{mac}}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  dvipsnames,enabledeprecatedfontcommands]{scrartcl}
\title{Taking uncertainty in word embedding bias estimation seriously: a
bayesian approach}
\author{Alicja Dobrzeniecka and Rafal Urbaniak}
\date{}

@@

Modern Natural Language Processing (NLP) models are used to complete
various tasks such as providing email filters, smart assistants, search
results, language translations, text analytics and so on. All of them
need as an input words represented by means of numbers which is
accomplished with word embeddings, in which particular lexical units are
represented as vectors of real numbers.

\begin{itemize}
\item
  troche o tym jak sa skonstruowane (optimizing for co-ocurrence
  frequency)
\item
  przejrzec jak to jest wprowadzane w kilku innych artykulach, zwl. fair
  is better than sensational
\item
  troche wiecej o tej konstrukcji i intuicji semantycznych, ale to nie
  super dobry pomysl
\item
  undesirable bias with respect to a certain groups words if
  stereotypically connected words (for stereotypes that we don't want to
  be used or relied on in downstream tasks) are systematically closer to
  each other. + EXAMPLES
\end{itemize}

It has been suggested {[}1--6{]} that in the learning process such
models can learn implicit biases that reflect harmful stereotypical
thinking. A large chunk of the literature on the topic focuses on the
geometry of the learnt word embeddings; in particular, unusually low
(cosine) proximity of words belonging, intuitively, to a stereotype, is
taken as a sign that this stereotype has been built into a given
embedding. This methodology will be in the focus of our paper.

@@

\hypertarget{weat-and-mac}{%
\subsection{WEAT and MAC}\label{weat-and-mac}}

@@

\hypertarget{methodological-problems-with-cosine-based-measures-of-bias}{%
\subsection{Methodological problems with cosine-based measures of
bias}\label{methodological-problems-with-cosine-based-measures-of-bias}}

@@

\hypertarget{metrics-that-pre-average-are-a-bad-guide}{%
\subsection{Metrics that pre-average are a bad
guide}\label{metrics-that-pre-average-are-a-bad-guide}}

@@

\vspace{1mm}
\footnotesize

\begin{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft4_files/figure-latex/unnamed-chunk-1-1} \end{center}
\caption{dsds}
\label{fig:weat7google}
\end{figure}

### 2022-07-28 paperDraft/paperDraft5.Rmd
results added to v 7

---
title: 'Taking uncertainty in word embedding bias estimation seriously: a  bayesian
  approach'
author: "Alicja Dobrzeniecka and Rafal Urbaniak"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    includes:
      in_header: Rafal_latex7.sty
  html_document:
    df_print: paged
classoption: dvipsnames,enabledeprecatedfontcommands, twocolumn
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/cosineReferences1.bib
csl: ../references/transactions-on-computational-logic.csl
---

@@

## WEAT

## MAC

>>>>

---
title: 'Taking uncertainty in word embedding bias estimation seriously: a  bayesian
  approach'
author: "Alicja Dobrzeniecka and Rafal Urbaniak"
output:
  pdf_document:
    number_sections: yes
    df_print: kable
    keep_tex: yes
    includes:
      in_header: Rafal_latex7.sty
  html_document:
    df_print: paged
classoption: dvipsnames,enabledeprecatedfontcommands
fontsize: 10pt
documentclass: scrartcl
urlcolor: blue
bibliography: ../references/cosineReferences1.bib
csl: ../references/transactions-on-computational-logic.csl
---

@@

\vspace{1mm}
\footnotesize
```{r generate plots,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", message = FALSE, warning = FALSE, results = FALSE}
source("functions/cleanDataset.R")
source("functions/plotFromPrecis.R")

weat7Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_7_google.csv")[,-1])
precisWeat7Google <- readRDS("resultsDFs/Weat7GoogleDF.rds")
resultsWeat7Google <- plotFromPrecis(precis = precisWeat7Google,
                                     dataset = weat7Google,
                                     list = "Weat 7",
                                     embedding = "Google")

weat7Glove <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_7_glove.csv")[,-1])
precisWeat7Glove <- readRDS("resultsDFs/Weat7GloveDF.rds")
resultsWeat7Glove <- plotFromPrecis(precis = precisWeat7Glove,
                                     dataset = weat7Glove,
                                     list = "Weat 7",
                                     embedding = "Glove")

weat7Reddit <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_7_reddit.csv")[,-1])
precisWeat7Reddit <- readRDS("resultsDFs/Weat7RedditDF.rds")
resultsWeat7Reddit <- plotFromPrecis(precis = precisWeat7Reddit,
                                    dataset = weat7Reddit,
                                    list = "Weat 7",
                                    embedding = "Reddit", ylims = c(.5,1.3))

weat1Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_google.csv")[,-1])
precisWeat1Google <- readRDS("resultsDFs/Weat1GoogleDF.rds")
resultsWeat1Google <- plotFromPrecis(precis = precisWeat1Google,
                                     dataset = weat1Google,
                                     list = "Weat 1",
                                     embedding = "Google")

weat1Glove <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_glove.csv")[,-1])
precisWeat1Glove <- readRDS("resultsDFs/Weat1GloveDF.rds")
resultsWeat1Glove <- plotFromPrecis(precis = precisWeat1Glove,
                                     dataset = weat1Glove,
                                     list = "Weat 1",
                                     embedding = "Glove")

weat1Reddit <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_reddit.csv")[,-1])
precisWeat1Reddit <- readRDS("resultsDFs/Weat1RedditDF.rds")
resultsWeat1Reddit <- plotFromPrecis(precis = precisWeat1Reddit,
                                     dataset = weat1Reddit,
                                     list = "Weat 1",
                                     embedding = "Reddit")

religionGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_google_dataset.csv")[,-1])
precisReligionGoogle <- readRDS("resultsDFs/ReligionGoogleDF.rds")
resultsReligionGoogle <- plotFromPrecis(precis = precisReligionGoogle,
                                     dataset = religionGoogle,
                                     list = "Religion",
                                     embedding = "Google")

religionGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_glove_dataset.csv")[,-1])
precisReligionGlove <- readRDS("resultsDFs/ReligionGloveDF.rds")
resultsReligionGlove <- plotFromPrecis(precis = precisReligionGlove,
                                        dataset = religionGlove,
                                        list = "Religion",
                                        embedding = "Glove")

religionReddit <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_reddit_dataset.csv")[,-1])
precisReligionReddit <- readRDS("resultsDFs/ReligionRedditDF.rds")
resultsReligionReddit <- plotFromPrecis(precis = precisReligionReddit,
                                       dataset = religionReddit,
                                       list = "Religion",
                                       embedding = "Reddit")

raceGoogle <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_google_dataset.csv")[,-1])
precisRaceGoogle <- readRDS("resultsDFs/RaceGoogleDF.rds")
resultsRaceGoogle <- plotFromPrecis(precis = precisRaceGoogle,
                                        dataset = raceGoogle,
                                        list = "Race",
                                        embedding = "Google")

raceGlove <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_glove_dataset.csv")[,-1])
precisRaceGlove <- readRDS("resultsDFs/RaceGloveDF.rds")
resultsRaceGlove <- plotFromPrecis(precis = precisRaceGlove,
                                    dataset = raceGlove,
                                    list = "Race",
                                    embedding = "Glove")

raceReddit <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_reddit_dataset.csv")[,-1])
precisRaceReddit <- readRDS("resultsDFs/RaceRedditDF.rds")
resultsRaceReddit <- plotFromPrecis(precis = precisRaceReddit,
                                    dataset = raceReddit,
                                    list = "Race",
                                    embedding = "Reddit")

genderGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_google_dataset.csv")[,-1])
precisGenderGoogle <- readRDS("resultsDFs/GenderGoogleDF.rds")
resultsGenderGoogle <- plotFromPrecis(precis = precisGenderGoogle,
                                    dataset = genderGoogle,
                                    list = "Gender",
                                    embedding = "Google")

genderGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_glove_dataset.csv")[,-1])
precisGenderGlove <- readRDS("resultsDFs/GenderGloveDF.rds")
resultsGenderGlove <- plotFromPrecis(precis = precisGenderGlove,
                                      dataset = genderGlove,
                                      list = "Gender",
                                      embedding = "Glove")

genderReddit <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_reddit_dataset.csv")[,-1])
precisGenderReddit <- readRDS("resultsDFs/GenderRedditDF.rds")

resultsGenderReddit <- plotFromPrecis(precis = precisGenderReddit,
                                     dataset = genderReddit,
                                     list = "Gender",
                                     embedding = "Reddit",  ylims = c(.4,1.2))

```

\begin{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsWeat7Google$plotJoint
```
\caption{dsds}
\label{fig:weat7google}
\end{figure}

### 2022-07-28 paperDraft/paperDraft6.tex
results added to v 7

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft5_files/figure-latex/unnamed-chunk-1-1} \end{center}
\caption{dsds}
\label{fig:weat7google}
\end{figure}

>>>>

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-1-1} \end{center}
\caption{dsds}
\label{fig:weat7google}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-2-1} \end{center}
\caption{dsds}
\label{fig:weat7glove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-3-1} \end{center}
\caption{dsds}
\label{fig:weat7reddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-4-1} \end{center}
\caption{dsds}
\label{fig:weat1google}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-5-1} \end{center}
\caption{dsds}
\label{fig:weat1glove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-6-1} \end{center}
\caption{dsds}
\label{fig:weat1reddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-7-1} \end{center}
\caption{dsds}
\label{fig:religionGoogle}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-8-1} \end{center}
\caption{dsds}
\label{fig:religionGlove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-9-1} \end{center}
\caption{dsds}
\label{fig:religionReddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-10-1} \end{center}
\caption{dsds}
\label{fig:raceGoogle}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-11-1} \end{center}
\caption{dsds}
\label{fig:raceGlove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-12-1} \end{center}
\caption{dsds}
\label{fig:raceReddit}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-13-1} \end{center}
\caption{dsds}
\label{fig:genderGoogle}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-14-1} \end{center}
\caption{dsds}
\label{fig:genderGlove}
\end{figure}

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-15-1} \end{center}
\caption{dsds}
\label{fig:genderReddit}
\end{figure}

### 2022-07-28 paperDraft/paperDraft7.Rmd
results added to v 7

\vspace{1mm}
\footnotesize
```{r generate plots,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "100%", message = FALSE, warning = FALSE, results = FALSE}
source("functions/cleanDataset.R")
source("functions/plotFromPrecis.R")

weat7Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_7_google.csv")[,-1])
precisWeat7Google <- readRDS("resultsDFs/Weat7GoogleDF.rds")
resultsWeat7Google <- plotFromPrecis(precis = precisWeat7Google,
                                     dataset = weat7Google,
                                     list = "Weat 7",
                                     embedding = "Google")

@@

weat1Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_google.csv")[,-1])
precisWeat1Google <- readRDS("resultsDFs/Weat1GoogleDF.rds")
resultsWeat1Google <- plotFromPrecis(precis = precisWeat1Google,
                                     dataset = weat1Google,
                                     list = "Weat 1",
                                     embedding = "Google")

weat1Glove <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_glove.csv")[,-1])
precisWeat1Glove <- readRDS("resultsDFs/Weat1GloveDF.rds")
resultsWeat1Glove <- plotFromPrecis(precis = precisWeat1Glove,
                                     dataset = weat1Glove,
                                     list = "Weat 1",
                                     embedding = "Glove")

weat1Reddit <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_reddit.csv")[,-1])
precisWeat1Reddit <- readRDS("resultsDFs/Weat1RedditDF.rds")
resultsWeat1Reddit <- plotFromPrecis(precis = precisWeat1Reddit,
                                     dataset = weat1Reddit,
                                     list = "Weat 1",
                                     embedding = "Reddit")

religionGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_google_dataset.csv")[,-1])
precisReligionGoogle <- readRDS("resultsDFs/ReligionGoogleDF.rds")
resultsReligionGoogle <- plotFromPrecis(precis = precisReligionGoogle,
                                     dataset = religionGoogle,
                                     list = "Religion",
                                     embedding = "Google")

religionGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_glove_dataset.csv")[,-1])
precisReligionGlove <- readRDS("resultsDFs/ReligionGloveDF.rds")
resultsReligionGlove <- plotFromPrecis(precis = precisReligionGlove,
                                        dataset = religionGlove,
                                        list = "Religion",
                                        embedding = "Glove")

@@

raceGoogle <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_google_dataset.csv")[,-1])
precisRaceGoogle <- readRDS("resultsDFs/RaceGoogleDF.rds")
resultsRaceGoogle <- plotFromPrecis(precis = precisRaceGoogle,
                                        dataset = raceGoogle,
                                        list = "Race",
                                        embedding = "Google")

raceGlove <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_glove_dataset.csv")[,-1])
precisRaceGlove <- readRDS("resultsDFs/RaceGloveDF.rds")
resultsRaceGlove <- plotFromPrecis(precis = precisRaceGlove,
                                    dataset = raceGlove,
                                    list = "Race",
                                    embedding = "Glove")

@@

genderGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_google_dataset.csv")[,-1])
precisGenderGoogle <- readRDS("resultsDFs/GenderGoogleDF.rds")
resultsGenderGoogle <- plotFromPrecis(precis = precisGenderGoogle,
                                    dataset = genderGoogle,
                                    list = "Gender",
                                    embedding = "Google")

genderGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_glove_dataset.csv")[,-1])
precisGenderGlove <- readRDS("resultsDFs/GenderGloveDF.rds")
resultsGenderGlove <- plotFromPrecis(precis = precisGenderGlove,
                                      dataset = genderGlove,
                                      list = "Gender",
                                      embedding = "Glove")

@@

resultsGenderReddit <- plotFromPrecis(precis = precisGenderReddit,
                                     dataset = genderReddit,
                                     list = "Gender",
                                     embedding = "Reddit",  ylims = c(.4,1.2))

@@

>>>>

\vspace{1mm}
\footnotesize
```{r generate plots,echo=FALSE,eval=TRUE,fig.align = "center",cache=FALSE, fig.show = "hold", out.width = "100%", message = FALSE, warning = FALSE, results = FALSE}
source("functions/cleanDataset.R")
source("functions/plotFromPrecis.R")

weat7Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_7_google.csv")[,-1])
precisWeat7Google <- readRDS("resultsDFs/Weat7GoogleDF.rds")
resultsWeat7Google <- plotFromPrecis(precis = precisWeat7Google,
                                     dataset = weat7Google,
                                     list = "Weat 7",
                                     embedding = "Google",
                                     ylims = c(.75,1.1))

@@

weat1Google <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_google.csv")[,-1])
precisWeat1Google <- readRDS("resultsDFs/Weat1GoogleDF.rds")
resultsWeat1Google <- plotFromPrecis(precis = precisWeat1Google,
                                     dataset = weat1Google,
                                     list = "Weat 1",
                                     embedding = "Google",
                                     ylims = c(.8,1.05))

weat1Glove <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_glove.csv")[,-1])
precisWeat1Glove <- readRDS("resultsDFs/Weat1GloveDF.rds")
resultsWeat1Glove <- plotFromPrecis(precis = precisWeat1Glove,
                                     dataset = weat1Glove,
                                     list = "Weat 1",
                                     embedding = "Glove",
                                     ylims = c(.75,1.2))

weat1Reddit <- cleanDataset(read.csv("./datasets/macWeatDatasets/weat_1_reddit.csv")[,-1])
precisWeat1Reddit <- readRDS("resultsDFs/Weat1RedditDF.rds")
resultsWeat1Reddit <- plotFromPrecis(precis = precisWeat1Reddit,
                                     dataset = weat1Reddit,
                                     list = "Weat 1",
                                     embedding = "Reddit",
                                      ylims = c(.5,1.1))

religionGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_google_dataset.csv")[,-1])
precisReligionGoogle <- readRDS("resultsDFs/ReligionGoogleDF.rds")
resultsReligionGoogle <- plotFromPrecis(precis = precisReligionGoogle,
                                     dataset = religionGoogle,
                                     list = "Religion",
                                     embedding = "Google",
                                      ylims = c(.65,1.05))

religionGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/religion_group_glove_dataset.csv")[,-1])
precisReligionGlove <- readRDS("resultsDFs/ReligionGloveDF.rds")
resultsReligionGlove <- plotFromPrecis(precis = precisReligionGlove,
                                        dataset = religionGlove,
                                        list = "Religion",
                                        embedding = "Glove",
                                        ylims = c(.7,1.1))

@@

raceGoogle <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_google_dataset.csv")[,-1])
precisRaceGoogle <- readRDS("resultsDFs/RaceGoogleDF.rds")
resultsRaceGoogle <- plotFromPrecis(precis = precisRaceGoogle,
                                        dataset = raceGoogle,
                                        list = "Race",
                                        embedding = "Google",
                                     ylims = c(.8,1.1))

raceGlove <-  cleanDataset(read.csv("./datasets/macWeatDatasets/race_group_glove_dataset.csv")[,-1])
precisRaceGlove <- readRDS("resultsDFs/RaceGloveDF.rds")
resultsRaceGlove <- plotFromPrecis(precis = precisRaceGlove,
                                    dataset = raceGlove,
                                    list = "Race",
                                    embedding = "Glove",
                                    ylims = c(.7,1.1))

@@

genderGoogle <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_google_dataset.csv")[,-1])
precisGenderGoogle <- readRDS("resultsDFs/GenderGoogleDF.rds")
resultsGenderGoogle <- plotFromPrecis(precis = precisGenderGoogle,
                                    dataset = genderGoogle,
                                    list = "Gender",
                                    embedding = "Google",
                                     ylims = c(.6,1.05))

genderGlove <- cleanDataset(read.csv("./datasets/macWeatDatasets/gender_group_glove_dataset.csv")[,-1])
precisGenderGlove <- readRDS("resultsDFs/GenderGloveDF.rds")
resultsGenderGlove <- plotFromPrecis(precis = precisGenderGlove,
                                      dataset = genderGlove,
                                      list = "Gender",
                                      embedding = "Glove",
                                      ylims = c(.5,1.1))

@@

resultsGenderReddit <- plotFromPrecis(precis = precisGenderReddit,
                                     dataset = genderReddit,
                                     list = "Gender",
                                     embedding = "Reddit",  ylims = c(.4,1.1))

@@

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsWeat7Glove$plotJoint
```
\caption{dsds}
\label{fig:weat7glove}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsWeat7Reddit$plotJoint
```
\caption{dsds}
\label{fig:weat7reddit}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsWeat1Google$plotJoint
```
\caption{dsds}
\label{fig:weat1google}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsWeat1Glove$plotJoint
```
\caption{dsds}
\label{fig:weat1glove}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsWeat1Reddit$plotJoint
```
\caption{dsds}
\label{fig:weat1reddit}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsReligionGoogle$plotJoint
```
\caption{dsds}
\label{fig:religionGoogle}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsReligionGlove$plotJoint
```
\caption{dsds}
\label{fig:religionGlove}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsReligionReddit$plotJoint
```
\caption{dsds}
\label{fig:religionReddit}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsRaceGoogle$plotJoint
```
\caption{dsds}
\label{fig:raceGoogle}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsRaceGlove$plotJoint
```
\caption{dsds}
\label{fig:raceGlove}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsRaceReddit$plotJoint
```
\caption{dsds}
\label{fig:raceReddit}
\end{figure}

```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsGenderGoogle$plotJoint
```
\caption{dsds}
\label{fig:genderGoogle}
\end{figure}

\begin{figure}
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsGenderGlove$plotJoint
```
\caption{dsds}
\label{fig:genderGlove}
\end{figure}

\begin{figure}
```{r,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "110%", dpi = 300}
resultsGenderReddit$plotJoint
```
\caption{dsds}
\label{fig:genderReddit}
\end{figure}

### 2022-07-28 paperDraft/paperDraft7.tex
results added to v 7

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-1-1} \end{center}
\caption{dsds}
\label{fig:weat7google}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-2-1} \end{center}
\caption{dsds}
\label{fig:weat7glove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-3-1} \end{center}
\caption{dsds}
\label{fig:weat7reddit}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-4-1} \end{center}
\caption{dsds}
\label{fig:weat1google}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-5-1} \end{center}
\caption{dsds}
\label{fig:weat1glove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-6-1} \end{center}
\caption{dsds}
\label{fig:weat1reddit}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-7-1} \end{center}
\caption{dsds}
\label{fig:religionGoogle}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-8-1} \end{center}
\caption{dsds}
\label{fig:religionGlove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-9-1} \end{center}
\caption{dsds}
\label{fig:religionReddit}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-10-1} \end{center}
\caption{dsds}
\label{fig:raceGoogle}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-11-1} \end{center}
\caption{dsds}
\label{fig:raceGlove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-12-1} \end{center}
\caption{dsds}
\label{fig:raceReddit}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-13-1} \end{center}
\caption{dsds}
\label{fig:genderGoogle}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-14-1} \end{center}
\caption{dsds}
\label{fig:genderGlove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft6_files/figure-latex/unnamed-chunk-15-1} \end{center}
\caption{dsds}
\label{fig:genderReddit}
\end{figure}

>>>>

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-1-1} \end{center}
\caption{dsds}
\label{fig:weat7google}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-2-1} \end{center}
\caption{dsds}
\label{fig:weat7glove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-3-1} \end{center}
\caption{dsds}
\label{fig:weat7reddit}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-4-1} \end{center}
\caption{dsds}
\label{fig:weat1google}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-5-1} \end{center}
\caption{dsds}
\label{fig:weat1glove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-6-1} \end{center}
\caption{dsds}
\label{fig:weat1reddit}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-7-1} \end{center}
\caption{dsds}
\label{fig:religionGoogle}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-8-1} \end{center}
\caption{dsds}
\label{fig:religionGlove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-9-1} \end{center}
\caption{dsds}
\label{fig:religionReddit}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-10-1} \end{center}
\caption{dsds}
\label{fig:raceGoogle}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-11-1} \end{center}
\caption{dsds}
\label{fig:raceGlove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-12-1} \end{center}
\caption{dsds}
\label{fig:raceReddit}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-13-1} \end{center}
\caption{dsds}
\label{fig:genderGoogle}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-14-1} \end{center}
\caption{dsds}
\label{fig:genderGlove}
\end{figure}

@@

\begin{center}\includegraphics[width=1.1\linewidth]{paperDraft7_files/figure-latex/unnamed-chunk-15-1} \end{center}
\caption{dsds}
\label{fig:genderReddit}
\end{figure}
